My Cool Title

### 2019-05-05 paper.tex
Added sections on previous work, added more references to bib

>>>>

Making a mobile device that can detect objects and guide a PwVI in real-time and using on-board processing power has become much more feasible in recent years, thanks to improvements to mobile computing power and image processing methods.
Early attempts to solve this guidance problem made use of special markers or barcodes, encoded with object or environmental information, and a smartphone that can efficiently scan the environment for these simple patterns~\cite{gude2013blind,iannizzotto2005badge3d,manduchi2012mobile}. 
The device then uses some feedback mode (e.g.\ voice, Braille) to read out the embedded information or guide the user towards the markers. 
Improvements to feature detectors and deep networks have made it more viable~\cite{redmon2016you,huang2017speed} to replace the markers with real objects, while providing the same guidance functionality.
The SIFT and SURF-based systems in~\cite{schauerte2012assistive} is an example of a markerless system.
An alternative detection approach proposed in~\cite{bigham2010vizwiz}, and commercialised in the `Be My Eyes' app~\cite{bemyeyes2019}, requires the user to send a photo of their environment and target object to a Mechanical Turk worker or volunteer that then sends the position of the requested object within the picture back to the user.

The issue with the marker-based approach is that it requires a significant amount of effort to place and maintain markers around an environment.
This problem is remedied in the markerless systems.
However, both of these approaches are passive in their guidance approach and rely on the user placing the desired marker/object within the camera's view by themselves first before any guidance can be provided. 
The human-based systems from~\cite{bigham2010vizwiz,bemyeyes2019} can leverage a human's understanding of the environment to help guide a person to the correct area, but the drawback here is that there is a significant lag time and a significant reliance on a good internet connection and remote worker being available. 
Our previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing a controller that provides the user with instructions on where to point the device to find an out of view object and we proved that this is a viable method to search for an object. 
However, this work relied upon physical barcodes, encoded with object information, to simulate real objects.
In this work, we are replacing the barcodes with real objects, thereby closing the object detection and guidance loop.

\todo{Object detectors}
